\begin{itemize}
    \setlength\itemsep{0.3em}

    \item Awarded \textbf{Best Bachelor Degree in Computer Science}  for receiving the highest overall mark when I graduated Aberystwyth University in 2015. My dissertation, \emph{Online Dispute Resolution for Maritime Collisions}, also won the British Computer Society Prize for the \textbf{Best Major Project}.

    \item Awarded \textbf{Best Contributor of the Year} at the BBC News Developer Awards 2015, for my contributions to our most-starred open source project: Wraith. The Developer Awards are an internal, department-wide, peer-voted awards ceremony.

    \item \textbf{Travelled to India and Indonesia to recruit specialist developers} for BBC World Service expansion. I've been trained in fair selection, have screened CVs and code tests and have organised and ran interviews for  software engineers of all levels.

    \item \textbf{Published an article in  Smashing Magazine}, outlining my efficient manual-testing strategy - the ``Three Phase Attack'' - devised during my time as a Test Engineer at the BBC:
    \\\url{smashingmagazine.com/2016/02/high-impact-minimal-effort-cross-browser-testing}

    \item I \textbf{set up my own company} while at university. Webdapper Ltd has developed over 10 websites, and generated over 20,000 Facebook likes for its clients through advertising campaigns.
    
    \item \textbf{I'm a tenor in the \emph{BBC Symphony Chorus}} and have performed at internationally televised concerts. Previously: \emph{National Youth Choir of Wales} (two years), \emph{Elizabethan Madrigal Singers} (two years plus one year as Choral Director).

\end{itemize}
