\begin{itemize}
    \setlength\itemsep{0.3em}
    
    \item \textbf{Technical leadership} – devised and implemented an abstraction strategy to deliver Visual Journalism content across BBC products, third-party sites and platforms (AMP, FIA, Apple News) with minimal development overhead. Led the team's upgrade to a componentised ES6/SCSS/Handlebars architecture, resulting in lower development time and more robust and consistent content.
    
    \item\textbf{Accessibility} - promote accessible web design and development at the BBC through my voluntary role as ``Accessibility Champion''. I apply progressive enhancement in all of my projects, building up from a core experience of semantic HTML and aria-roles and ensuring that experiences are acceptable whatever your browser or input (including screen readers).

    \item \textbf{Communication skills} - led my team's adoption of user stories as a communication tool and test specification, rooting out complexity early and saving countless hours of wasted effort. Championed the need for a Pattern Library for better team collaboration and shared vocabulary. Used JIRA in my side company to manage tasks. Have given well-received presentations to technical and non-technical audiences at all levels.

    \item \textbf{Testing} – lead maintainer of the Wraith visual regression testing tool, which has gone on to become the BBC's most-starred open-source project. Highly adept at authoring declarative Cucumber features alongside clean, reusable Ruby step definitions. Hand-built an in-house BDD framework in Node. Set up suites of automated tests in Docker on Jenkins CI. Regularly develop in a TDD way (Mocha/Chai, Jasmine, PHPUnit).

    \item \textbf{Line management} – I look after six people in my latest role, helping them define and achieve objectives and working with the technical project manager to assign work which align with their goals.

\end{itemize}
